Phase paper outline your mom last night

### 2014-05-22 Manuscript/Phase_detectors_outline.tex
add citation for phase variability

\subsection*{Physiological data}
\begin{itemize}
\item Renal cortical perfusion
	\begin{itemize}
	\item phase synchronization among regions of the kidney
	\end{itemize}
\item Blood pressure and heart rate
	\begin{itemize}
	\item [Phase lag between changes in blood pressure and changes in heart rate] \hfill \\
	The oscillations of blood pressure and heart rate are often compared using cross-spectral analyses to quantify baroreflex function.  With this method, the coherence, transfer function gain, and phase relationship between the two signals are quantified.  The phase shift between blood pressure and heart rate is lengthened in some pathophysiological conditions (Javorka et al, 2011) and more variable/unstable in other conditions (Halamek et al, 2003 Circulation).  Therefore, the phase relationship between these two signals might be an important outcome measure for cardiovascular testing.  
	\end{itemize}
\item Something about SCG or ECG ?
\item Cerebral blood flow ?
\end{itemize}

>>>>

\subsection*{Physiological data}
\begin{itemize}
\item Renal cortical perfusion
	\begin{itemize}
	\item phase synchronization among regions of the kidney
	\end{itemize}
\item Blood pressure and heart rate
	\begin{itemize}
	\item [Phase lag between changes in blood pressure and changes in heart rate] \hfill \\
	The oscillations of blood pressure and heart rate are often compared using cross-spectral analyses to quantify baroreflex function.  With this method, the coherence, transfer function gain, and phase relationship between the two signals are quantified.  The phase shift between blood pressure and heart rate is lengthened in some pathophysiological conditions (Javorka et al, 2011) and more variable/unstable in other conditions (Halamek et al, 2003 Circulation; Stewart et al., 2000).  Therefore, the phase relationship between these two signals is an important outcome measure for cardiovascular testing.  
	\end{itemize}
\item Something about SCG or ECG ?
\item Cerebral blood flow ?
\end{itemize}
